Compositional equivalences based on Open pNets

### 2020-03-16 2016-Weak-FH-Bisim/WeakBisim.tex
typo and style example

%\TODO{Eric: rewrite example with new Protocolkeep only OT1, and adapt comments}
\begin{example}\emph{An open-transition.}
  \label{OT:SimpleProt}
At the upper level, the $SimpleSystem$ pNet of Figure \ref{SimpleProt:Impl} has 2 holes and $SimpleProtocol$ as
a subnet, itself containing 3 pLTSs. One of its possible open transitions
(synchronizing the hole $P$
with the $Sender$ within the \emph{SimpleProtocol}) is:

>>>>

%\TODO{Eric: rewrite example with new Protocolkeep only OT1, and adapt comments}
\begin{example}[An open-transition]
  \label{OT:SimpleProt}
At the upper level, the $\symb{SimpleSystem}$ pNet of Figure \ref{SimpleProt:Impl} has 2 holes and $\symb{SimpleProtocol}$ as
a subnet, itself containing 3 pLTSs. One of its possible open transitions
(synchronizing the hole $P$
with the $\symb{Sender}$ within the \emph{SimpleProtocol}) is:
